Select-based random access \\ to variable-byte encodings

### 2020-05-24 gradu/gradu.tex
Adds a few updates
Adds more text
Final fixes

\usepackage{lmodern}         % Font package, again in some systems.
\usepackage{textcomp}        % Package for special symbols
\usepackage[pdftex]{color, graphicx} % For pdf output and jpg/png graphics
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage[pdftex, plainpages=false]{hyperref} % For hyperlinks and pdf metadata
\usepackage{fancyhdr}        % For nicer page headers
\usepackage{tikz}             % For making vector graphics (hard to learn but powerful)
\usetikzlibrary{arrows.meta,scopes,chains,matrix}
%\usepackage{wrapfig}        % For nice text-wrapping figures (use at own discretion)
\usepackage{amsmath, amssymb} % For better math
\usepackage{algorithm}  
\usepackage[noend]{algpseudocode}
\usepackage{pgfplots} 
\singlespacing               %line spacing options; normally use single

@@

% Set supervisors and examiners, use the titles according to the thesis language
% Prof. 
% Dr. or in Finnish toht. or tri or FT, TkT, Ph.D. or in Swedish... 
\supervisors{Prof.~D.U.~Mind, Dr.~O.~Why}
\examiners{Prof.~D.U.~Mind, Dr.~O.~Why}

@@

Enormous datasets are a common occurence today and compressing them is often beneficial. Fast direct access to any element in the compressed data is a requirement in the field of compressed 
data structures, which is not possible with traditional compression methods.

Variable-byte encoding is a method for compressing integers of different byte lengths. It removes unused leading bytes and adds an additional \textit{continuation bit} to each byte to 
denote whether the compressed integer continues to the next byte or not. An existing solution using \textsc{rank} data structure performs well in this given task. This thesis introduces an 
alternative solution using \textsc{select} data structure and compares the two implementations. An experimentation is also done on retrieving a subarray from the compressed data structure.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\backmatter
%\begin{appendices}

@@

%\end{appendices}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\usepackage{lmodern}         % Font package, again in some systems.
\usepackage{textcomp}        % Package for special symbols
\usepackage[pdftex]{color, graphicx} % For pdf output and jpg/png graphics
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage[pdftex, plainpages=false]{hyperref} % For hyperlinks and pdf metadata
\usepackage{fancyhdr}        % For nicer page headers
\usepackage{tikz}             % For making vector graphics (hard to learn but powerful)
\usetikzlibrary{arrows.meta,scopes,chains,matrix}
%\usepackage{wrapfig}        % For nice text-wrapping figures (use at own discretion)
\usepackage{amsmath, amssymb} % For better math
\usepackage{algorithm}  
\usepackage[noend]{algpseudocode}
\usepackage{pgfplots} 
\usepackage{cleveref}
\singlespacing               %line spacing options; normally use single

@@

% Set supervisors and examiners, use the titles according to the thesis language
% Prof. 
% Dr. or in Finnish toht. or tri or FT, TkT, Ph.D. or in Swedish... 
\supervisors{Dr.~Simon~Puglisi, Dr.~Juha~Kärkkäinen}
\examiners{Dr.~Simon~Puglisi, Dr.~Juha~Kärkkäinen}

@@

Enormous datasets are a common occurence today and compressing them is often beneficial. Fast direct access to any element in the compressed data is a requirement in the field of compressed 
data structures, which is not easily supported with traditional compression methods.

Variable-byte encoding is a method for compressing integers of different byte lengths. It removes unused leading bytes and adds an additional \textit{continuation bit} to each byte to 
denote whether the compressed integer continues to the next byte or not. An existing solution using a \textit{rank} data structure performs well in this given task. This thesis introduces an 
alternative solution using a \textit{select} data structure and compares the two implementations. An experimentation is also done on retrieving a subarray from the compressed data structure.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\backmatter
\begin{appendices}

@@

\end{appendices}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
